---
title: "R Notebook"
output: html_notebook
---
```{r}
print("Hey!")
```

## Here is markdown 

```{r}
plot(cars)
x <- sample(1:100, 1000, replace=TRUE)
hist(x)

x <- rnorm(100, mean=0, sd=1)
y <- x + rnorm(100, mean=0, sd=1)
plot(x,y)

x.s <- sort(x)
y.s <- sort(y)
plot(x.s, y.s); lines(x.s, y.s); abline(a=0, b=1, col="red")

#browseVignettes()
install.packages("tidyverse")

#library(ggplot2)
#ggplot(data=diamonds) + geom_histogram(binwidth=500, aes(x=price)) + ggtitle("Diamond Price Distribution") + xlab("Diamond Price U$") + ylab("Frequency") + theme_minimal()
#ggplot(diamonds, aes(x=carat,y=price)) + geom_point()
#ggplot(diamonds, aes(x=carat,y=price, color=clarity)) + geom_point()

#ggplot(diamonds, aes(x=carat,y=price, color=clarity, shape=cut)) + geom_point()

#ggplot(diamonds, aes(x=carat,y=price, color=clarity, shape=cut)) + geom_point() + facet_wrap(~ cut)

#ggplot(diamonds, aes(x=carat,y=price, color=clarity, shape=cut)) + geom_point() + facet_wrap(~ cut, nrow=5)

#ggplot(diamonds, aes(x=carat,y=price, color=clarity, shape=cut)) + geom_point() + facet_wrap(~ cut, nrow=5)

#ggplot(diamonds, aes(x=carat,y=price)) + geom_point() + geom_smooth()

#ggplot(diamonds, aes(x=carat,y=price, color=clarity)) + geom_point() + geom_smooth()

#ggplot(diamonds, aes(x=carat,y=price, color=clarity)) + geom_point() + geom_smooth()
#ggplot(diamonds, aes(x=carat,y=price, color=clarity)) + geom_point() + geom_smooth(method="lm")

#help(geom_smooth, ggplot2)

### ######################################### Exercise 1

### Importing Data
library(readr)
data <- read_csv("EconomistData.csv")
data


## Ploting basic scatter plot
library(ggplot2)

##Exercise 1

# Q1
ggplot(data, aes(x=CPI, y=HDI)) + geom_point()

# Q2
ggplot(data, aes(x=CPI, y=HDI)) + geom_point(size=2, color="blue")

# Q3
ggplot(data, aes(x=CPI, y=HDI, color=Region)) + geom_point()

# Q4
ggplot(data, aes(x=CPI, y=HDI, color=Region)) + geom_point(size=2)

# Q5
ggplot(data, aes(x=CPI, y=HDI, color=Region)) + geom_point(size=data$HDI.Rank/mean(data$HDI.Rank))


##Exercise 2

# Q1
ggplot(data, aes(x=CPI, y=HDI)) + geom_point()

# Q2
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_smooth()

# Q3
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_smooth(method="lm")
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_smooth(method="loess")
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_smooth(method="gam", formula = y ~s(x))

# Q4
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_line(color='steelblue', size=2)
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_line(alpha=0.5)

# Q5
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + geom_smooth(method="loess", span = 0.95)


## Exercise 3
# Q1
ggplot(data, aes(x=CPI, y=HDI, color=Region)) + geom_point()

# Q2
ggplot(data, aes(x=CPI, y=HDI, color=Region)) + geom_point() + labs(x= "Corruption Perception Index", y= "Human Development Index")

# Q2
ggplot(data, aes(x=CPI, y=HDI)) + geom_point() + labs(x= "Corruption Perception Index", y= "Human Development Index") + scale_colour_manual(values = c("blue", "green", "yellow", "magenta", "red", "black"))

# Q3
ggplot(data, aes(x=CPI, y=HDI)) + geom_point(aes(colour = Region)) + scale_colour_manual(values = c("blue", "green", "yellow", "orange", "red", "black"))

list.files(readr_example(""))

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

